---
title: "Airbnb Pricing Analysis in Berlin"
author: "Junqian Zhang"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Description
```{r, echo=FALSE, warning=FALSE}
library(dplyr)
data <- read.csv('listings_berlin.csv')
#data<- dplyr::filter(data, neighbourhood_group != "Reinickendorf" & neighbourhood_group != "Treptow - Köpenick")
data <- dplyr::select(data, -c('id', 'name', 'host_id', 'host_name', 'neighbourhood', 'neighbourhood_group','reviews_per_month', 'last_review'))
data <- na.omit(data) 
summary(data)
```

## Normality Check of Dependent Variable
```{r, echo=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(ggpubr)
data <- dplyr::filter(data, price > (mean(data$price) - 3* sd(data$price)) & price < (mean(data$price) + 3* sd(data$price)))
data <- dplyr::filter(data, price > 0)
data$logprice = log(data$price)
summary(data$price)
price_n <- ggdensity(data, x = "price", fill = "lightgray", title = "Price") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")
logprice_n <- ggdensity(data, x = "logprice", fill = "lightgray", title = "Price") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")
figure_n <- ggarrange(price_n, logprice_n, ncol=2, nrow=1)
figure_n
```
## Data Distribution and Correlation
```{r, echo=FALSE, warning=FALSE}
quantile(data$minimum_nights, 0.99)
quantile(data$number_of_reviews, 0.99)
quantile(data$calculated_host_listings_count, 0.99)
quantile(data$availability_365, 0.99)
data <- filter(data, minimum_nights <= 100)
data <- filter(data, number_of_reviews <= 244)
data <- filter(data, calculated_host_listings_count <= 44)
data <- filter(data, availability_365 <= 365)
library(corrplot)
cors <- cor(cbind(price = data$price, dplyr::select(data, -c('room_type', 'logprice', 'price'))))
corrplot(cors, type = "upper",tl.col = "black", tl.srt = 45, method='number')
library(PerformanceAnalytics)
chart.Correlation(cbind(price = data$logprice, dplyr::select(data, -c('room_type', 'price', 'logprice'))), histogram=TRUE, pch=20)
```

## Relation between logprice and location
```{r, echo=FALSE, warning=FALSE}
library(raster)
library(ggplot2)
#germany <- getData(country = "Germany", level = 1) 
#map <- ggplot() +
#  geom_polygon(data = germany,
#               aes(x = long, y = lat, group = group),
#               colour = "grey10", fill = "#fff7bc") + ylim(52.3,52.7) + xlim(13.08,13.77)+theme(panel.background = element_blank())+ theme(axis.title.x=element_blank(),
#        axis.text.x=element_blank(),
#        axis.ticks.x=element_blank())+theme(axis.title.y=element_blank(),
#        axis.text.y=element_blank(),
#        axis.ticks.y=element_blank())
berlin_background <- png::readPNG("berlin.png")
ggplot(data, aes(x=longitude, y=latitude, col= logprice)) + background_image(berlin_background) + geom_point(size=1)+ ylim(52.3,52.7) + xlim(13.08,13.77)
```


## Relation between Room type and Price
```{r, echo=FALSE, warning=FALSE}
library(car)
library(plyr)
vv <- as.vector(unique(data$room_type))
data$room_type <- factor(data$room_type, levels = vv, labels = vv, ordered = FALSE)
ggplot(data, aes(x = room_type, y = price)) +
    geom_boxplot() + stat_summary(fun.y = median, geom = 'line', group= 1, color= "orange", size = 1.2)+ annotate("text", x = 1:length(table(data$room_type)), y = aggregate(price ~ room_type, data, median)[ , 2], label = table(data$room_type),col = "black", vjust=-1) + xlab("Room Type") + ylab("Price")+ ylim(0,500)
summary(aov(price ~ room_type, data=data))
ddply(data,~room_type,summarise,mean=mean(price),sd=sd(price),n=length(price))
```
## Difference between Private room and Shared room
```{r, echo=FALSE, warning=FALSE}
library(ggpubr)
set.seed(42)
private <- dplyr::filter(data, room_type=="Private room")
private$id <- seq(1,7835,1)
private <- private[match(sample(unique(private$id),206),private$id),]
shared <-  dplyr::filter(data, room_type=="Shared room")
t.test(private$logprice, shared$logprice, alternative = "two.sided", var.equal = FALSE)
```

## Data Splitting
```{r, echo=FALSE, warning=FALSE}
library(caret)
set.seed(42)
data$price <- NULL
train_indices<- createDataPartition(data$logprice,p=0.7,list=FALSE)
dtrain <- data[train_indices,]
dtest <- data[-train_indices,]
pp <- preProcess(dtrain, method = "range")
dtrain_scale <- predict(pp, dtrain)
dtest_scale <- predict(pp, dtest)
eval_results <- function(true, predicted, df) {
    SSE <- sum((predicted - true)^2)
    SST <- sum((true - mean(true))^2)
    R_square <- round(1 - SSE / SST,4)
    RMSE = round(sqrt(SSE/nrow(df)),4)
    # Model performance metrics
    data.frame(
        RMSE = RMSE,
        Rsquare = R_square
    )
}
```

# Mulitple Linear Regression

## Full Model
```{r, echo=FALSE, warning=FALSE}
full <- lm(logprice~.,data = dtrain)
summary(full)
eval_results(dtest$logprice, predict(full, dtest), dtest)
```

## Regression with Forward Stepwise Method
```{r, echo=FALSE, warning=FALSE}
library(leaps)
regfit.fwd=regsubsets(logprice~.,data=dtrain,method="forward")
summary.fwd <- summary(regfit.fwd)
plot(summary.fwd$bic,xlab="Number of Variables",ylab="bic")
points(which.min(summary.fwd$bic),summary.fwd$bic[which.min(summary.fwd$bic)],pch=20,col="red")
```

```{r, echo=FALSE, warning=FALSE}
plot(regfit.fwd, scale = 'bic')
grid(nx=10,ny=8,col="grey",lty = "solid")
abline(h=8, col="orange", lwd = 10)
text(8,7, "Optimal Model", col="orange",cex = 0.8)
```

```{r, echo=FALSE, warning=FALSE}
model1 <- lm(logprice~., data =dplyr::select(dtrain, -c('latitude', 'longitude')))
summary(model1)
eval_results(dtest$logprice, predict(model1, dtest), dtest)
```
```{r, echo=FALSE, warning=FALSE}
par(mfrow=c(2,2))
plot(model1)
```
## Collinearity
```{r, echo=FALSE, warning=FALSE}
library(car)
vif(model1)
```

```{r, echo=FALSE, warning=FALSE}
library(MASS)
robust <- rlm(logprice ~ ., data = dplyr::select(dtrain, -c('latitude', 'longitude')))
summary(robust)
eval_results(dtest$logprice, predict(robust, dtest), dtest)
```

```{r, echo=FALSE, warning=FALSE}
hweights <- data.frame(resid = robust$resid, weight = robust$w)
hweights2 <- hweights[order(robust$w), ]
hweights2[11564:11573, ]
hweights2[1:10, ]
```


# Decision Tree

```{r, echo=FALSE, warning=FALSE}
library(rpart)
library(rpart.plot)
set.seed(42)
tree <- rpart(logprice~.,data=dtrain, method = "anova")
printcp(tree)
plotcp(tree)
rpart.plot(tree)
eval_results(dtest$logprice, predict(tree, dtest), dtest)
```
## Random Forest
```{r, echo=FALSE, warning=FALSE}
library(randomForest)
library(vip) 
library(pdp)
set.seed(42)
rf = randomForest(logprice ~., data = dtrain, ntree=1000)
rf
plot(rf)
vip(rf, num_features = 7, bar = FALSE)
eval_results(dtest$logprice, predict(rf, dtest), dtest)
```




